Output Summary

### 2021-10-22 03-post-process/output-plots.Rmd
Update vcov_decomp() code in RMD

```{r vcov-decomp, message = FALSE}
# Convert the precision matrices monitored by JAGS into the marginal SD and correlation matrix terms
# postpack::vcov_decomp() does this for all posterior samples

Sig_Lphi_O0_O1_post = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", invert = FALSE, sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))

# make the labels/indices for which elements of the vcov matrices contain unique covariances
# no point in summarizing/displaying both off-diagonal triangles
dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
vcov_cols = dummy_cols[lower.tri(dummy_cols)]
vcov_rows = dummy_rows[lower.tri(dummy_rows)]
vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "]")

# subset out only the unique elements
Sig_Lphi_O0_O1_post = post_subset(Sig_Lphi_O0_O1_post, c("sig", paste0("rho.+", vcov_indices)))

# combine these derived posterior samples with the main object
post = post_bind(post, Sig_Lphi_O0_O1_post)
```

>>>>

```{r vcov-decomp, message = FALSE}
# Convert the precision/covariance matrices monitored by JAGS into the marginal SD and correlation matrix terms
# postpack::vcov_decomp() does this for all posterior samples
Sig_lPb = suppressMessages(vcov_decomp(post, "Sig_lPb", sigma_base_name = "sig_lPb", rho_base_name = "rho_lPb"))
Sig_Lpi = suppressMessages(vcov_decomp(post, "Sig_Lpi", sigma_base_name = "sig_Lpi", rho_base_name = "rho_Lpi"))
Sig_Lphi_Pa_Mb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Pa_Mb[.,.,1]"), "Sig_Lphi_Pa_Mb", sigma_base_name = "sig_Lphi_Pa_Mb", rho_base_name = "rho_Lphi_Pa_Mb"))
Sig_Lphi_Pa_Mb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Pa_Mb[.,.,2]"), "Sig_Lphi_Pa_Mb", sigma_base_name = "sig_Lphi_Pa_Mb", rho_base_name = "rho_Lphi_Pa_Mb"))
Sig_Lphi_Mb_Ma1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Mb_Ma[.,.,1]"), "Sig_Lphi_Mb_Ma", sigma_base_name = "sig_Lphi_Mb_Ma", rho_base_name = "rho_Lphi_Mb_Ma"))
Sig_Lphi_Mb_Ma2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lphi_Mb_Ma[.,.,2]"), "Sig_Lphi_Mb_Ma", sigma_base_name = "sig_Lphi_Mb_Ma", rho_base_name = "rho_Lphi_Mb_Ma"))
Sig_Lphi_Ma_O0 = suppressMessages(vcov_decomp(post, "Sig_Lphi_Ma_O0", sigma_base_name = "sig_Lphi_Ma_O0", rho_base_name = "rho_Lphi_Ma_O0"))
Sig_Lphi_O0_O1 = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))
Sig_Lpsi_O1_Rb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O1_Rb[.,.,1]"), "Sig_Lpsi_O1_Rb", sigma_base_name = "sig_Lpsi_O1_Rb", rho_base_name = "rho_Lpsi_O1_Rb"))
Sig_Lpsi_O1_Rb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O1_Rb[.,.,2]"), "Sig_Lpsi_O1_Rb", sigma_base_name = "sig_Lpsi_O1_Rb", rho_base_name = "rho_Lpsi_O1_Rb"))
Sig_Lpsi_O2_Rb1 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O2_Rb[.,.,1]"), "Sig_Lpsi_O2_Rb", sigma_base_name = "sig_Lpsi_O2_Rb", rho_base_name = "rho_Lpsi_O2_Rb"))
Sig_Lpsi_O2_Rb2 = suppressMessages(vcov_decomp(rm_index(post, "Sig_Lpsi_O2_Rb[.,.,2]"), "Sig_Lpsi_O2_Rb", sigma_base_name = "sig_Lpsi_O2_Rb", rho_base_name = "rho_Lpsi_O2_Rb"))
Sig_Lphi_Rb_Ra = suppressMessages(vcov_decomp(post, "Sig_Lphi_Rb_Ra", sigma_base_name = "sig_Lphi_Rb_Ra", rho_base_name = "rho_Lphi_Rb_Ra"))
Sig_Lphi_Sb_Sa = suppressMessages(vcov_decomp(post, "Sig_Lphi_Sb_Sa", sigma_base_name = "sig_Lphi_Sb_Sa", rho_base_name = "rho_Lphi_Sb_Sa"))

# update node names for quantities that have a third dimension to the covariance matrix (origin or LH type)
Sig_Lphi_Pa_Mb1 = add_index(Sig_Lphi_Pa_Mb1, c("sig", "rho"), 1)
Sig_Lphi_Pa_Mb2 = add_index(Sig_Lphi_Pa_Mb2, c("sig", "rho"), 2)
Sig_Lphi_Mb_Ma1 = add_index(Sig_Lphi_Mb_Ma1, c("sig", "rho"), 1)
Sig_Lphi_Mb_Ma2 = add_index(Sig_Lphi_Mb_Ma2, c("sig", "rho"), 2)
Sig_Lpsi_O1_Rb1 = add_index(Sig_Lpsi_O1_Rb1, c("sig", "rho"), 1)
Sig_Lpsi_O1_Rb2 = add_index(Sig_Lpsi_O1_Rb2, c("sig", "rho"), 2)
Sig_Lpsi_O2_Rb1 = add_index(Sig_Lpsi_O2_Rb1, c("sig", "rho"), 1)
Sig_Lpsi_O2_Rb2 = add_index(Sig_Lpsi_O2_Rb2, c("sig", "rho"), 2)

# make the labels/indices for which elements of the vcov matrices contain unique covariances
# no point in summarizing/displaying both off-diagonal triangles
dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
vcov_cols = dummy_cols[lower.tri(dummy_cols)]
vcov_rows = dummy_rows[lower.tri(dummy_rows)]
vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "(,.)?]")

# subset out only the unique elements
Sig_lPb = post_subset(Sig_lPb, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lpi = post_subset(Sig_Lpi, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lphi_Pa_Mb1 = post_subset(Sig_Lphi_Pa_Mb1, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lphi_Pa_Mb2 = post_subset(Sig_Lphi_Pa_Mb2, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lphi_Mb_Ma1 = post_subset(Sig_Lphi_Mb_Ma1, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lphi_Mb_Ma2 = post_subset(Sig_Lphi_Mb_Ma2, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lphi_Ma_O0 = post_subset(Sig_Lphi_Ma_O0, c("sig", "rho.+"))
Sig_Lphi_O0_O1 = post_subset(Sig_Lphi_O0_O1, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lpsi_O1_Rb1 = post_subset(Sig_Lpsi_O1_Rb1, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lpsi_O1_Rb2 = post_subset(Sig_Lpsi_O1_Rb2, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lpsi_O2_Rb1 = post_subset(Sig_Lpsi_O2_Rb1, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lpsi_O2_Rb2 = post_subset(Sig_Lpsi_O2_Rb2, c("sig", paste0("rho.+", vcov_indices)))
Sig_Lphi_Rb_Ra = post_subset(Sig_Lphi_Rb_Ra, c("sig", "rho.+"))
Sig_Lphi_Sb_Sa = post_subset(Sig_Lphi_Sb_Sa, c("sig", paste0("rho.+", vcov_indices)))

# combine these derived posterior samples with the main object
post = post_bind(post, Sig_lPb)
post = post_bind(post, Sig_Lpi)
post = post_bind(post, Sig_Lphi_Pa_Mb1)
post = post_bind(post, Sig_Lphi_Pa_Mb2)
post = post_bind(post, Sig_Lphi_Mb_Ma1)
post = post_bind(post, Sig_Lphi_Mb_Ma2)
post = post_bind(post, Sig_Lphi_Ma_O0)
post = post_bind(post, Sig_Lphi_O0_O1)
post = post_bind(post, Sig_Lpsi_O1_Rb1)
post = post_bind(post, Sig_Lpsi_O1_Rb2)
post = post_bind(post, Sig_Lpsi_O2_Rb1)
post = post_bind(post, Sig_Lpsi_O2_Rb2)
post = post_bind(post, Sig_Lphi_Rb_Ra)
post = post_bind(post, Sig_Lphi_Sb_Sa)
```
